Impact of interaction network structure on community-level plant reproduction success

### 2019-01-17 paper_round2.Rmd
small changes in partial residual plots

#best model is m1, plot significant variable, in this case degree

>>>>

#best model is m1, plot significant variable, in this case degree, do partial residual plots to show the effect of that variable in isolation of the others

crPlots(m1, smooth=FALSE, terms = ~  norm_degree.sc, main = "", ylab = "Fruitset", col.lines= "black", pch=19, col= "black", bg = "darkgrey", cex=2, cex.axis=1.2, cex.lab=1.5, 
        xlab = "Pollinator species diversity")  #PROBLEM HERE BECAUSE OF RANDOM EFFECTS, NEED TO CHECK!

#or do original plots, no partial residuals
